---
title: "Big Rapids Garden Tour 2018"
subtitle: "General Federation of Women's Clubs"
author: "Carrie Franklund"
output:
  word_document: default
  sansfont: Arial
  pdf_document: 
    latex_engine: xelatex
  html_document:
    df_print: paged
---
\setmonofont{Arial}
\setsansfont{Arial}
\setromanfont{Arial}

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
theData <- read_xlsx("GFWC.xlsx", na="NA")
```


## Garden Tour Data

A total of `r nrow(theData)` surveys were completed following the 2018 GFWC Garden Tour. 

## Advertising Effectiveness

```{r publicity, echo=FALSE, fig.width=8, fig.height=6}
heard <- colSums(theData[,1:5])
heard[["Other"]] <- sum(!is.na(theData$Other))
heard <- as.vector(heard)
names(heard) <- c("Pioneer", "Tri-County Shopper", "Pioneer Shopper", "Radio", "Friend", "Other")
par(mar=c(10,5,.5,.5))
barplot(heard, las=2, ylim=c(0,50), ylab="Number of Votes", xlab="", col = "dodgerblue4")
mtext("Source", side=1, line=8)
text(x=c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7),y=heard+1.5 , as.character(heard))
box()
```


```{r table1, echo=FALSE, results='as-is'}

theData[!is.na(theData$Other), 6]

```

## Day Preference
```{r days, echo=FALSE, fig.width=8, fig.height=6}
days <- colSums(theData[,17:23])
barplot(days, las=1, ylab="Number of Votes", xlab="Day of the Week", col = "dodgerblue4", ylim = c(0,50))
text(x=c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7, 7.9),y=days+1.5 , as.character(days))
segments(1.4,45,4.8,45, col="dodgerblue4", lwd=6)
text(x=3.1, y=47, "Preferred", cex=1.2)

box()
```


## Time Preference
```{r times, echo=FALSE, fig.width=8, fig.height=6}
times <- colSums(theData[,9:16])
barplot(times, las=1, ylab="Number of Votes", xlab="Time (PM)", col = "dodgerblue4", ylim = c(0,50))
text(x=c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7, 7.9, 9.1),y=times+1.5 , as.character(times))
segments(1.4,45,8.5,45, col="dodgerblue4", lwd=6)
text(x=5.1, y=47, "Preferred", cex=1.2)
box()
```


## Best Features


## Opportunities for Improvement  
There were only `r sum(!is.na(theData$Least))` suggestions made in response to the "least favorite part" prompt. Of these...


## Recruiting Effectiveness  
A total of `r sum(theData$Interested=="Yes", na.rm=TRUE)` people (`r round(sum(theData$Interested=="Yes", na.rm=TRUE)/nrow(theData)*100,1)`%) indicated that they would like to learn more about GFWC. 
